\chapter{The effect of an S-wave on the angular analysis of \BdToKpill}
\label{chap:swave:theo}

\emph{This chapter is the work of the author except where referenced. This work was published in Ref~\cite{Blake:2012mb}. 
This work was based on Ref.~\cite{LHCb-CONF-2012-008} and uses different values for the angular observables than were measured in the previous chapter. 
This does not affect the conclusions of this chapter since the size of the bias comes from the size of the dilution factor coming from the \kpi S-wave contribution.
%The size of the S-wave contribution used is independant of the measured central values of the angular observables.
}

\input{chapter6/intro}

\input{chapter6/theory}

\input{chapter6/observables}

\input{chapter6/toys}

\input{chapter6/analysis}

\input{chapter6/measurement}

\input{chapter6/isobar}

\section{Conclusions}

In summary, the inclusion of a resonant \kpi S-wave in the angular 
analysis of \BdToKstll  has been formalised and the complete angular 
distribution for both an S and P wave state described.
The inclusion of an S-wave state has an overall dilution
 effect on the theoretical observables.
The impact of an S-wave on an angular analysis is evaluated using toy 
Monte Carlo events.
The S-wave contribution can only be ignored for datasets of 
less than 200 events, meaning the angular observables measured in 
the \qsq bin between 4.3 and 8.68 \gevgevcccc and between
1 and 6 \gevgevcccc measured in Chapter 5 may be affected.
The bias on the angular observables incurred by assuming a pure P-wave
 \kpi state can be removed by including the S-wave in the angular distribution. 
The degradation in resolution on the angular observables 
from fitting a more complicated angular 
distribution can be minimised by performing the 
fit in a wide region around the $\Kstarz(892)$ resonance.
However, the parameterisation of the \mkpi spectrum also requires consideration 
of the background component in the wider \mkpi window which may increase the complexity
 and contribute other biases to measurements of the angular observables.




