

\begin{quote}
\emph{There is a theory which states that if ever anyone discovers exactly what the Universe is for 
and why it is here, it will instantly disappear and be replaced by something even more bizarre and inexplicable.
There is another theory which states that this has already happened.} \\
- Douglas Adams, \emph{The Restaurant at the End of the Universe} (1980)
\end{quote}


\emph{In the beginning the Universe was created.
This has made a lot of people very angry and has been widely regarded as a bad move}
- Douglas Adams, \emph{The Restaurant at the End of the Universe} (1980)


\emph{“Isn't it enough to see that a garden is beautiful without having to believe that there 
are fairies at the bottom of it too?” } 
- Douglas Adams

\emph{“So long, and thanks for all the fish.”} 
- Douglas Adams

\emph{“We demand rigidly defined areas of doubt and uncertainty!”} 
- Douglas Adams


\emph{“Well, I mean, yes idealism, yes the dignity of pure research, yes the pursuit of truth in all its forms, 
but there comes a point I'm afraid where you begin to suspect that the entire multidimensional infinity of 
the Universe is almost certainly being run by a bunch of maniacs. And if it comes to a choice between spending 
yet another ten million years finding that out, and on the other hand just taking the money and running, 
then I for one could do with the exercise.” }
- Douglas Adams, The Hitchhiker's Guide to the Galaxy

\emph{“I love deadlines. I like the whooshing sound they make as they fly by.” } 
- Douglas Adams

\emph{"Space is big. You just won't believe how vastly, hugely, mind- bogglingly big it is.
 I mean, you may think it's a long way down the road to the chemist's, but that's just peanuts to space."}
- Douglas Adams, The Hitchhiker's Guide to the Galaxy

\emph{“We'll be saying a big hello to all intelligent lifeforms everywhere and 
to everyone else out there, the secret is to bang the rocks together, guys.”}
- Douglas Adams, The Hitchhiker's Guide to the Galaxy


\emph{“In the beginning there was nothing, which exploded.”}
― Terry Pratchett, Lords and Ladies



\emph{ - "What're quantum mechanics?" \\ 
- "I don't know. People who repair quantums, I suppose." }
-- (Terry Pratchett, Eric)



\emph{it was here that the thaum, hitherto believed to be the smallest possible particle of mag-
ic, was succesfully demonstrated to be made up of /resons/ (Lit.: 'Thing-ies') or reality
fragments. Currently research indicates that each reson is itself made up of a combina-
tion of at least five 'flavours', known as 'up', 'down', 'sideways', 'sex appeal' and
'peppermint'.}
-- (Terry Pratchett, Lords and Ladies)


\emph{“Well, I mean, yes idealism, yes the dignity of pure research, yes the pursuit of truth in all its forms, 
but there comes a point I'm afraid where you begin to suspect that the entire multidimensional infinity of 
the Universe is almost certainly being run by a bunch of maniacs. 
%And if it comes to a choice between spending 
%yet another ten million years finding that out, and on the other hand just taking the money and running, 
%then I for one could do with the exercise.
” }
- Douglas Adams, The Hitchhiker's Guide to the Galaxy

\emph{"While I'm still confused and uncertain, it's on a much higher plane, d'you see, and at
least I know I'm bewildered about the really fundamental and important facts of the
universe."
Treatle nodded. "I hadn't looked at it like that," he said, "But you're absolutely right. He's
really pushed back the boundaries of ignorance."}
-- Discworld scientists at work
(Terry Pratchett, Equal Rites)

\begin{quotation}
\emph{it was here that the thaum, hitherto believed to be the smallest possible particle of 
magic, was succesfully demonstrated to be made up of /resons/ (Lit.: 'Thing-ies') or reality
fragments. Currently research indicates that each reson is itself made up of a combination
 of at least five 'flavours', known as 'up', 'down', 'sideways', 'sex appeal' and
'peppermint'.}
-- (Terry Pratchett, Lords and Ladies)
\end{quotation}


